---
title: "Pokémon Analysis"
subtitle: "Application Overview"
author: "Rafael Gurgel"
date: "08/02/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(plotly)
library(data.table)
library(ggpubr)
library(tidyr)
library(cluster)
library(ggdendro)
library(DT)
```

## Introduction
Course Project of Developing Data Products: Application to analyse (superficially) Pokemóns Generations and Types. 

The data is get from [Serebii](https://www.serebii.net), cleaned, processed resulting in the following data. (You can check the code [here](https://github.com/rafagurgel/Rpokemon).)

```{r}
pokemon <- unique(fread("pokemon.csv"))
pokemon <- pokemon[-671,]

datatable(pokemon[,1:12], options = list(lengthMenu = c(1, 2), pageLength = 5, scrollX = TRUE))
#str(pokemon[,1:12])
```

## Generation Progression
Qualitatively we can notice that the attributes increased over the generations. [Check in the app](https://rafaelgurgel.shinyapps.io/pokemon/)

```{r, fig.height=4, fig.width=7}
g1<- ggplot(pokemon, aes(factor(Generation), Total)) + 
    geom_boxplot(fill = "#4271AE", colour = "#1F3552",alpha = 0.7) +
    geom_smooth(method = "lm", se=T, aes(group=1),colour = "red") +
    theme_bw()+
    ylab('Total') +
    xlab('Generation')+
    ggtitle("Total over Generations")

g1
```

## Types Comparison
Dragon Pokémons look stronger than Bug types

```{r}
poke<- pokemon%>%
    select(Total,Type.1,Type.2)
poke1 <- poke%>%
    filter(Type.1 == "Bug" | Type.2 == "Bug" )%>%
    select(Total)%>%
    mutate(Type = "Bug")
poke2 <- poke%>%
    filter(Type.1 == "Dragon" | Type.2 ==  "Dragon" )%>%
    select(Total)%>%
    mutate(Type = "Dragon")
poke <- rbind(poke1,poke2)

p <- ggplot(poke, aes(Total, fill = factor(Type))) + 
    geom_density(alpha = 0.2) +
    theme_bw() +
    ylab('Density') +
    xlab('Total Attributes')+
    ggtitle("Bug vs Dragon Total Stats") + 
    theme(legend.position="bottom")
p
```

## Dendogram
An extra thing that I made to try to classify the Pokémons.
```{r fig.height=6, warning=FALSE}
poke<- pokemon%>%
    unique()%>%
    filter(Generation == 1)%>%
    gather(tmp,Type,starts_with("Type."),na.rm = TRUE)%>%
    mutate(tmp = TRUE)%>%
    spread(Type,tmp,fill = FALSE)

poke<- poke %>% mutate(Attack = apply(cbind(Attack,Special.Attack), 1, max),Defense = apply(cbind(Defense,Special.Defense), 1, max))%>% select(-Special.Attack, -Special.Defense)
rownames(poke)<- poke$Pokemon
poke<- poke%>%select(-c(1,3))



hc <- hclust(dist(poke), method = "average")

dendr <- dendro_data(hc, type="rectangle") 

p<- ggplot() + 
    geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend)) + 
    geom_text(data=label(dendr), aes(x=x, y=y, label=label, hjust=0), size=1.2) +
    coord_flip() + scale_y_reverse(expand=c(0.2, 0)) + 
    theme(axis.line.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_blank(),
          axis.title.y=element_blank(),
          panel.background=element_rect(fill="white"),
          panel.grid=element_blank()
          )
p
```